WordRec Experiment

### 2019-04-12 Data_and_analysis/analyses.Rmd
more revisions

parameters <- coef_s %>%
  right_join(coef_c) %>%
  right_join(coef_j) %>%
  select(experiment, bias_s, var_s, bias_c, var_c, bias_j, var_j_s, var_j_c)

>>>>

parameters <- coef_s %>%
  right_join(coef_c) %>%
  right_join(coef_j) %>%
  select(experiment, bias_s, var_s, bias_c, var_c, bias_j, var_j_s, var_j_c) %>%
  mutate(bias_s = - bias_s,
         bias_c = - bias_c, 
         bias_j = - bias_j)
